Clean 2015 Raw Data

### 2018-11-02 data-raw/README.Rmd
Replace more FLD with PDL

# Add treatment numbers --------------------------------------------------------
DS2015$TRT <- NA
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 0)] = "FLD_N0"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 100)] = "FLD_N100"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 120)] = "FLD_N120"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 0)] = "AWD_N0"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 100)] = "AWD_N100"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 120)] = "AWD_N120"

@@

# Add treatment numbers --------------------------------------------------------
DS2016$TRT <- NA
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 60)] = "FLD_N60"
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 180)] = "FLD_N180"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 60)] = "AWD_N60"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 180)] = "AWD_N180"

@@

RAW_data$TRT <-
  forcats::fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "FLD_N0",
    "FLD_N100",
    "FLD_N120",
    "FLD_N60",
    "FLD_N180"
  )

>>>>

# Add treatment numbers --------------------------------------------------------
DS2015$TRT <- NA
DS2015$TRT[which(DS2015$WMGT == "PDL" &
                   DS2015$NRTE == 0)] = "PDL_N0"
DS2015$TRT[which(DS2015$WMGT == "PDL" &
                   DS2015$NRTE == 100)] = "PDL_N100"
DS2015$TRT[which(DS2015$WMGT == "PDL" &
                   DS2015$NRTE == 120)] = "PDL_N120"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 0)] = "AWD_N0"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 100)] = "AWD_N100"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 120)] = "AWD_N120"

@@

# Add treatment numbers --------------------------------------------------------
DS2016$TRT <- NA
DS2016$TRT[which(DS2016$WMGT == "PDL" &
                   DS2016$NRTE == 60)] = "PDL_N60"
DS2016$TRT[which(DS2016$WMGT == "PDL" &
                   DS2016$NRTE == 180)] = "PDL_N180"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 60)] = "AWD_N60"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 180)] = "AWD_N180"

@@

RAW_data$TRT <-
  forcats::fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "PDL_N0",
    "PDL_N100",
    "PDL_N120",
    "PDL_N60",
    "PDL_N180"
  )
